---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pipertts

<!-- badges: start -->
[![R-CMD-check](https://github.com/muschellij2/pipertts/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/muschellij2/pipertts/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of `pipertts` is to wrap the [piper](https://github.com/rhasspy/piper) Python module for translation of text to other languages.

# Package Installation
You can install the development version of `pipertts` like so:

```r
remotes::install_github("muschellij2/pipertts")
```

To install `TTS`, you can either run `install_piper`, which calls `reticulate::py_install()`,  If you already have a `conda` environment enacted, use `reticulate::py_install` or simply `install_piper`:

```r
library(pipertts)
install_piper()
```

Or you can run `create_piper_condaenv()`, which calls `reticulate::conda_create()` and creates a `conda` environment for `piper`, named `piper`.

``` r
create_piper_condaenv()
```

If you use this method, you should run `reticulate::use_condaenv("piper")` before enabling Python.




## Example

This is a basic example which shows you how to solve a common problem:

```{r example, cache = TRUE}
library(pipertts)
model = tempfile(fileext = ".onnx")
config = tempfile(fileext = ".json")
res = piper_download_voice(voice = "ljspeech", quality = "high",
                           model = model, config = config)
voice = piper_voice(model = res$model, config = res$config)
text = c(
  "Who knows what it's like to be a human?  ", 
  "Definitely not me.  I'm a computer.  ", 
  "Just a silly computer, but I'm learning.  And when I learn, whew, watch out."
)
output = piper_synthesize(voice, text = text, sentence_silence = 0.2)
output
```


```{r play, eval = FALSE}
system2("play", output)
```
